\protect\hyperlink{main-content}{Skip to main content}

\hypertarget{pst-scroll-pixel-helper}{}

\emph{} Back to top

\emph{} {Ctrl+K}

{}

\href{../index.html}{}

mdof

Site Navigation

\begin{itemize}
\tightlist
\item
  \href{index.html}{Reference}
\item
  \href{../theory/index.html}{Theory}
\item
  \href{../examples/index.html}{Examples}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://github.com/BRACE2/mdof}{{\emph{}} {GitHub}}
\end{itemize}

{}

Site Navigation

\begin{itemize}
\tightlist
\item
  \href{index.html}{Reference}
\item
  \href{../theory/index.html}{Theory}
\item
  \href{../examples/index.html}{Examples}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://github.com/BRACE2/mdof}{{\emph{}} {GitHub}}
\end{itemize}

Section Navigation

\begin{itemize}
\tightlist
\item
  \href{index.html}{mdof modules and top-level functions}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \protect\hyperlink{}{mdof.markov module}
\item
  \href{mdof.realize.html}{mdof.realize module}
\item
  \href{mdof.modal.html}{mdof.modal module}
\item
  \href{mdof.transform.html}{mdof.transform module}
\end{itemize}

\hypertarget{rtd-footer-container}{}

\hypertarget{main-content}{}
\begin{itemize}
\tightlist
\item
  \href{../index.html}{\emph{}}
\item
  \href{index.html}{Reference}
\item
  mdof.markov module
\end{itemize}

\hypertarget{searchbox}{}

\hypertarget{module-mdof.markov}{}
\protect\hypertarget{mdof-markov-module}{}{}

\hypertarget{mdof.markov-module}{%
\section{\texorpdfstring{mdof.markov
module\protect\hyperlink{module-mdof.markov}{\#}}{mdof.markov module\#}}\label{mdof.markov-module}}

\begin{description}
\item[{ {{mdof.markov.}}{{okid}}{(}\emph{{{inputs}}},
\emph{{{outputs}}},
\emph{{{**}}{{options}}}{)}\protect\hyperlink{mdof.markov.okid}{\#}}]
Identify Markov parameters, or discrete impulse response data, for a
given set of input and output data. Observer Kalman Identification
Algorithm (OKID) \protect\hyperlink{id2}{{{[}}1{{]}}}.

\begin{description}
\item[Parameters{:}]
\begin{itemize}
\item
  \textbf{inputs} (\emph{array}) -- input time history. dimensions:
  {\textbackslash{}((q,nt)\textbackslash{})}, where
  {\textbackslash{}(q\textbackslash{})} = number of inputs, and
  {\textbackslash{}(nt\textbackslash{})} = number of timesteps
\item
  \textbf{outputs} (\emph{array}) -- output response history.
  dimensions: {\textbackslash{}((p,nt)\textbackslash{})}, where
  {\textbackslash{}(p\textbackslash{})} = number of outputs, and
  {\textbackslash{}(nt\textbackslash{})} = number of timesteps
\item
  \textbf{m} (\emph{int,} \emph{optional}) -- number of Markov
  parameters to compute. default: {\textbackslash{}(min(300,
  nt)\textbackslash{})}
\end{itemize}
\item[Returns{:}]
the Markov parameters, with dimensions
{\textbackslash{}((p,q,m+1)\textbackslash{})}
\item[Return type{:}]
array
\end{description}

\hypertarget{references}{}
\hypertarget{references}{%
\subsection{\texorpdfstring{References\protect\hyperlink{references}{\#}}{References\#}}\label{references}}

{{{[}}\protect\hyperlink{id1}{1}{{]}}}

Juang, J. N., Phan, M., Horta, L. G., \& Longman, R. W. (1993).
Identification of observer/Kalman filter Markov parameters-Theory and
experiments. Journal of Guidance, Control, and Dynamics, 16(2), 320-329.
(\url{https://doi.org/10.2514/3.21006})
\end{description}

\href{index.html}{\emph{}}

previous

Reference

\href{mdof.realize.html}{}

next

mdof.realize module

\emph{}

\emph{} On this page

\begin{itemize}
\tightlist
\item
  \protect\hyperlink{mdof.markov.okid}{\texttt{okid()}}
\end{itemize}

© Copyright 2023, Chrystal Chern.\\

Created using \href{https://www.sphinx-doc.org/}{Sphinx} 7.1.2.\\

Built with the
\href{https://pydata-sphinx-theme.readthedocs.io/en/stable/index.html}{PyData
Sphinx Theme} 0.14.1.
